\problemname{Yule Lads}

The kids in Iceland are pretty lucky. Not only do they have one Santa Claus,
but $N$ of them! They're called the Yule Lads, and on each of the $N$ nights
before Christmas, one of them comes to town, giving those that have been nice a
small present, and those that have been naughty a potato.

On a street in a small town in Iceland, there are $N$ houses, numbered
in turn from $1$ to $N$. Each house is beautifully decorated with
Christmas lights, and initially they are all turned on.

On each of the $N$ nights before Christmas, one of the Yule Lads visits this
street. The Yule Lad visiting $K$ nights before Christmas is very fond of the
number $K$, and will only visit the houses whose house number is
divisible\footnote{An integer $p$ is divisible by the integer $q$ if the
division $p/q$ leaves no remainder.} by $K$. Furthermore, the Yule Lads are
troublemakers, and will toggle the state of the Christmas lights on every house
that they visit (i.e.\ turning the lights off if they are on, or turning them
on if they are off).

However, some of the Yule Lads have been feeling sick, and did not come to
town. On Christmas day all but the first house had their lights turned on. How
many Yule Lads came to town?

\section*{Input}
The first line of input contains a positive integer $N$, the number of Yule
Lads and the number of houses in the street.

\section*{Output}
Output a single integer, the number of Yule Lads that came to town. You can
assume that there is only one scenario that leads to all houses having their
lights on except for house number $1$.

% Alternatively: It can be proved that there is a unique solution.

% Alternatively: If there are multiple valid solutions, output any of them.

\section*{Example}
Consider the case $N = 6$. Then there are six Yule Lads, and six houses in the
street. Here is what happens on each of the six nights before Christmas,
assuming that no Yule Lad is sick.

\begin{itemize}
    \item Six nights before Christmas, the Yule Lad will turn the lights at house $6$ off.
    \item Five nights before Christmas, the Yule Lad will turn the lights at house $5$ off.
    \item Four nights before Christmas, the Yule Lad will turn the lights at house $4$ off.
    \item Three nights before Christmas, the Yule Lad will turn the lights at house $3$ off, and the lights at house $6$ on.
    \item Two nights before Christmas, the Yule Lad will turn the lights at houses $2$ and $6$ off, and the lights at house $4$ on.
    \item The night before Christmas, the Yule Lad will turn the lights at houses $1$ and $4$ off, and the lights at houses $2$, $3$, $5$ and $6$ on.
\end{itemize}

However, house number $4$ has its lights off on Christmas day, contrary to what
actually happened.

On the other hand, if only the Yule Lad that was supposed to come into town
four days before Christmas is sick, then all lights, except for at house number
$1$, will be lit on Christmas day. The correct answer is thus $5$: Yule Lads
came to town $6$, $5$, $3$, $2$ and $1$ days before Christmas.

\section*{Grading}
Your solution will be graded on a set of subtasks.
A subtask will consist of multiple test cases.
To get the points for a subtask, your solution must pass all test cases that are part of the subtask.

% TODO: Feel free to redistribute points if you don't agree
\noindent
\begin{tabular}{| l | l | l |}
\hline
Subtask & Score & Constraints \\ \hline
1 & 15 & $N \leq 13$ \\ \hline
2 & 10 & $N \leq 1000$ \\ \hline
3 & 12 & $N \leq 10^5$ \\ \hline
4 & 13 & $N \leq 5 \cdot 10^{6}$ \\ \hline
5 & 15 & $N \leq 10^{8}$ \\ \hline
6 & 14 & $N \leq 10^{10}$ \\ \hline
7 & 21 & $N \leq 10^{13}$ \\ \hline
\end{tabular}

